Owl Occupancy in Three of El Salvador's Protected Areas from 2003 through 2013

### 2021-02-28 manuscript_working/ms_working_RMD.Rmd
removed abbreviations from figures (eg MOOW)

![2. Probability of occupancy ($\psi_{t,h}$) summarized by route for Ferruginous Pygmy-Owl (FEPO), Mottled Owl (MOOW), and Spectacled Owl (SPEO). Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2).  Posteriors were summarized with median $\pm$ 90% credible intervals. \label{psi_means}](../output/figures/psi_means-1.png)

![3. Probability of occupancy by route and year for Ferruginous Pygmy-Owl (FEPO), Mottled Owl (MOOW), and Spectacled Owl (SPEO). Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2). Posteriors were summarized with median $\pm$ 90% credible intervals. \label{figure2}](../output/figures/psi_byYr-1.png)

![4. Species richness (Richness*) by route and year. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2).  Posteriors of Richness* were summarized with median (black dot) $\pm$ 90% credible intervals (dark grey shading and vertical black lines). The number of owl species detected at each route and year was indicated with the light grey area. \label{figure5}](../output/figures/richness_byRtYr-1.png)

![5. The probabiliity of detecting owls during spontaneous surveys (i.e., pre-broadcast) and after broadcast, depending on the species of owl used for broadcast vocalization. These logistic regression coefficients were evaluated from the richness model, which combined all detected species (All Species) and the single-species occupancy models for Ferruginous Pygmy-Owls (FEPO), Mottled Owls (MOOW), and Spectacled Owls (SPEO). Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador. Posteriors were summarized with median $\pm$ 90% credible intervals. The pre-broadcase effect size's credible intervals are represented with two grey horizontal lines on each graph \label{figure6}](../output/figures/p_detection-1.png)

>>>>

![2. Probability of occupancy ($\psi_{t,h}$) summarized by route for Ferruginous Pygmy-Owl, Mottled Owl, and Spectacled Owl. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2).  Posteriors were summarized with median $\pm$ 90% credible intervals. \label{psi_means}](../output/figures/psi_means-1.png)

![3. Probability of occupancy by route and year for Ferruginous Pygmy-Owl, Mottled Owl, and Spectacled Owl. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2). Posteriors were summarized with median $\pm$ 90% credible intervals. \label{figure2}](../output/figures/psi_byYr-1.png)

![4. Species richness (Richness$^*$) by route and year. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2).  Posteriors of Richness$^*$ were summarized with median (black dot) $\pm$ 90% credible intervals (dark grey shading and vertical black lines). The number of owl species detected at each route and year was indicated with the light grey area. \label{figure5}](../output/figures/richness_byRtYr-1.png)

![5. The probabiliity of detecting owls during spontaneous surveys (i.e., pre-broadcast) and after broadcast, depending on the species of owl used for broadcast vocalization. These logistic regression coefficients were evaluated from the richness model, which combined all detected species (All Species) and the single-species occupancy models for Ferruginous Pygmy-Owls, Mottled Owls, and Spectacled Owls. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador. Posteriors were summarized with median $\pm$ 90% credible intervals. The pre-broadcase effect size's credible intervals are represented with two grey horizontal lines on each graph \label{figure6}](../output/figures/p_detection-1.png)
